Total CD4 Data

### 2019-05-30 Cytokine_Analysis.Rmd
Includes test about combining HC and LTBI

data<-read.csv("ICS_Donor_Info_clean.csv")
data$TB<-gsub("BCG|Unknown", "Naïve", data$TB)
data$TB<-factor(data$TB, levels=c("Naïve","Healthy Control","LTBI","Active TB"))
data$SM<-gsub("US|Not US|Unknown", "Naïve", data$SM)
data$SM<-factor(data$SM, levels=c("Naïve","Negative","Schisto+"))
Donor<-data
```
#P-values for Cytokine Comparisons

>>>>

data<-read.csv("ICS_Donor_Info_clean.csv")
data$TB<-gsub("BCG|Unknown", "Naïve", data$TB)
data$TB<-factor(data$TB, levels=c("Naïve","Healthy Control","LTBI","Active TB"))
data$SM<-gsub("US|Not US|Unknown", "Naïve", data$SM)
data$SM<-factor(data$SM, levels=c("Naïve","Negative","Schisto+"))
Donor<-data
```

#Can we use HC and LTBI together
```{r}
library(knitr)
#creates a list of character strings for each of the columns of interest
colnames<-names(dplyr::select(CD4, -X, -Sample, -Donor, -Stim, -TB, -SM))
for(col in colnames){#this will loop through each character string in the list
    a<-subset(CD4, CD4$Stim=="PMA") #subsets the data to only contain the unstimulated samples
    #inserts each character string into the column argument of the pvals function written above
    b<-pvals_hc(a, col)
    print(kable(b, caption=col))

    c<-filter(a, TB=="HC")
    #will return the output for each character string in the loop
    y<-plot_hc(c, "SM", col)
    d<-filter(a, TB %in% c("HC", "LTBI"))
    d$TB<-as.factor("combined")
    x<-plot_hc(d, "SM", col)
    grid.arrange(y,x, ncol=2)
    }
```

### 2019-05-30 ICS_CD4.Rmd
Includes test about combining HC and LTBI

>>>>

#Are HC and LTBI different or can we combine?

```{r}
library(knitr)
#creates a list of character strings for each of the columns of interest
colnames<-names(dplyr::select(cd4, -X, -Sample, -Donor, -Stim, -TB, -SM))
for(col in colnames){#this will loop through each character string in the list
    a<-subset(cd4, cd4$Stim=="UN") #subsets the data to only contain the unstimulated samples
    #inserts each character string into the column argument of the pvals function written above
    b<-pvals_hc(a, col)
    print(kable(b, caption=col))

    c<-filter(a, TB=="HC")
    #will return the output for each character string in the loop
    y<-plot_hc(c, "SM", col)
    d<-filter(a, TB %in% c("HC", "LTBI"))
    d$TB<-as.factor("combined")
    x<-plot_hc(d, "SM", col)
    grid.arrange(y,x, ncol=2)
    }
```
